Template for indicator documentation

### 2022-08-12 AndersTest.Rmd

<!-- This is a template for how to document the indicator analyses. 
Make a copy of this file and store it in the root folder (same as where this template is stored) folder. 
Name te file DRAFT_myIndicatorName.Rmd. 
Because this is also a stand-alone Rmd file inside a bookdown project, in order to knit the file for preview purposes,
you need to type rmarkdown::render("template.Rmd") in the console, 
as the the usual Ctrl + Alt + k will not work. When the analyses is complete,
Anders Kolstad, or someone else, will perform a rapid code review, making sure 
the analysis is repeatable by someone else. Be therefore very careful to annotate 
and comment on every step in the analysis. Se When completed, Anders will make a copy
of the working file and put it in the same project root folder, but removing the 'DRAFT_' part of the name. 
After modifying it slightly (mainly removing the top YAML header and updating the rmd_files argument in '_bookdown.yml') the output will become available 
on the website (https://ninanor.github.io/ecosystemCondition/). -->

<!-- Examples: For an example, see 'indicators/breareal-workingFile.Rmd'. Notice the degree of annotation.
Make sure also to not change the order, or modify the headers unless you really need to. This is because it
easier to read the web page as a whole of the indicators are presented using the same layout. 
To complete the exmaple, se 'breareal.Rmd' and notice how Anders has prepared the working file to become a
chapter in eth bookdown project. Anders will do this for you as patr of the code review.
-->

@@

#### Regions
<!-- In case you need to map the indicator value to regions, you can do that here -->
Importing a shape file with the regional delineation. 
```{r}
#reg <- st_read("data/regions.shp")
#st_crs(reg)
```

@@

### Eksport file (final product)
Export final file. Ideally a georeferenced shape or raster wit indicators values (raw and normalised), reference values and errors.

>>>>

This is a test

<!-- This is a template for how to document the indicator analyses.

Make a copy of this file and store it in the root folder (same as where this template is stored) folder. 
Name te file DRAFT_myIndicatorName.Rmd.

Because this is a stand-alone Rmd file inside a bookdown project, in order to knit the file for preview purposes,
you need to type rmarkdown::render("template.Rmd") in the console, 
as the the usual Ctrl + Alt + k will not work.

Make sure also to not change the order, or modify the headers, unless you really need to. This is because it
easier to read the web page as a whole of the indicators are presented using the same layout.

When the analyses is complete, Anders Kolstad, or someone else, will perform a rapid code review, making sure 
the analysis is repeatable by someone else. Be therefore very careful to annotate 
and comment on every step in the analysis. When completed, Anders will make a copy
of the working file and put it in the same project root folder, but removing the 'DRAFT_' part of the name. 
After modifying it slightly (mainly removing the top YAML header and updating the rmd_files argument in '_bookdown.yml') 
the output will become available on the website (https://ninanor.github.io/ecosystemCondition/). -->

<!-- Examples:

For an example, see 'indicators/breareal-workingFile.Rmd' 
and the subsequent 'breareal.Rmd' 
which again, when rendered, produces this:
https://ninanor.github.io/ecosystemCondition/areal-av-isbreer.html

Notice the degree of annotation.

-->

@@

#### Regions
<!-- In case you need to map the indicator value to regions, you can do that here. Remove this chapter if not relevant. -->
Importing a shape file with the regional delineation. 
```{r}
#reg <- sf::st_read("data/regions.shp")
#st_crs(reg)
```

@@

### Eksport file (final product)
<!-- Export final file. Ideally a georeferenced shape or raster wit indicators values (raw and normalised), reference values and errors. -->
